### 2015-07-05 intro-new.tex
Intro revision: edited placement, redir, routing

\section{Why placement is more powerful than redirection, routing}

(1) geo-distributed infrastructure and the locality in workloads,
means that low cost design is possible 
The primary reason content placement is effective is the geo-graphic and temporal locality observed in real world workloads. The locality makes it possible to make

, a particular content is popular only in a few regions at any given time.

Effective content placement is key to designing infrastructure services due to multiple reasons.

(1) It ensures that the average number of replicas of content is kept small, thereby \emph{reducing the infrastructure cost}.

(2) It leverages the geo-distributed deployment to select the location of these few replicas in regions of greater demand, which reduces average latency for the users.

(3) It exploits the fact that

 to provide low latencies for most of the users

Because of

(1)

(2) locations carefully leverages geo-distributed resources more effectively

Placement schemes exploit locality inherent in real world workloads by storings content at those times and at those locations where it is more popular. Thus, by reducing the number of replicas of content placement schmes reduce the cost for infrastructure services. Further, by selecting the locations based on demand, they also leverage geo-distributed resources.

"Cost, geo-distribution and locality are linked together"

Controls cost by making only a few replicas of a content

Placement makes use of geo-distibuted resources to reduce latency

Leverages locality to reduce user-perceived latencies

A key purpose of geo-distribution in infrastructure services is to maintain service deployment locations close to end-users.  Such deployments can reduce user-perceived latency only if the requested content is available at nearby locations. Content placement is powerful because it determines the availability of content at nearby locations, thereby deciding whether a geo-distributed deployment will be effective in reducing user-perceived latencies. We illustrate with a couple of examples why placement can be a more powerful degree of freedom than redirection and routing, and then explain why benefits of placement can be realized even with limited resources due to localiy in real-world workloads.

\subsection{Placement vs. redirection}

\begin{figure}
	\centering
	\includegraphics[scale=0.5]{fig/placement-vs-redirection.png}
	\caption{Placement vs. redirection: Content placement creates options for the redirection scheme to choose a nearby location for reducing user-perceived latencies.}	
	\label{fig:placement-redirection}
\end{figure}

Among the set of locations with the content, redirection chooses a location to send request. If the content is placed only at a far-away location, irrespective of how redirection is done, a user will observe a high latency to fetch content from the remote location. On the other hand, content placement can create more options to the redirection scheme to choose a location that is nearby. Thus, effective placement is a pre-requisite for a redirection scheme to provide low latencies.

\subsection{Placement vs. routing}

We briefly explain the \emph{traffic engineering} problem that is pertinent to our discussion of placement vs. routing. Traffic engineering computes network routing based on inputs of are the network topology, link capacities, and a \emph{traffic matrix}. The $i,j$-th entry in this matrix is the traffic from node $i$ to node $j$ in the network topology \cite{fortz2000internet}. A traffic engineering scheme computes routing to satisfy traffic demands while optimizing a cost function dependent on link utilization. For example, a common cost function is the maximum link utilization, MLU \cite{rexford}.

@@

Content placement is more powerful than routing because it can change the traffic matrix for which the routing is to be computed. Let us take an example traffic matrix for which routing is to be computed (Figure \ref{fig:placement-routing}). If all content that a node in a network needs is placed at the same node, there is no traffic to be sent to any other node, then the traffic matrix only as entries whose value is 0. The routing problem becomes trivial in this case.

%While this is an extreme example, and one may not have sufficient resources to place content at all locations in the network, this examples demonstrates that the ability to change the traffic matrix makes content placement more powerful than routing.

>>>>

\section{Why placement is more powerful than redirection, routing}
Content placement can achieve a good tradeoff between user -perceived latency and infrastructure cost due to geo-distribtued infrastructure and workload locality. Workload locality implies that a content is typically popular in only a few regions at any given time, and as a result only a few replicas of a content are sufficient to reduce user-perceived latency for most users. Further, the geo-distribued infrastructure enables these few replicas to be placed close to regions of demand, thereby reducing user-perceived latency as well as infrastructure cost. We illustrate with a couple of examples why placement can be a more powerful degree of freedom than redirection and routing in designing infrastructure services.

\begin{figure}

	\centering
	\includegraphics[scale=0.5]{fig/placement-vs-redirection.png}
	\caption{Placement vs. redirection: Content placement creates options for the redirection scheme to choose a nearby location for reducing user-perceived latencies.}	
	\label{fig:placement-redirection}
\end{figure}

\textbf{Placement vs. redirection:} Among the set of locations with the content, redirection chooses a location to send request. If the content is placed only at a far-away location, irrespective of how redirection is done, a user will observe a high latency to fetch content from the remote location. On the other hand, content placement can create more options to the redirection scheme to choose a location that is nearby. Thus, effective placement is a pre-requisite for a redirection scheme to provide low latencies.

%We briefly explain the \emph{traffic engineering} problem that is pertinent to our discussion of placement vs. routing. Traffic engineering computes network routing based on inputs of are the network topology, link capacities, and a \emph{traffic matrix}. A traffic engineering scheme computes routing to satisfy traffic demands while optimizing a cost function dependent on link utilization. For example, a common cost function is the maximum link utilization, MLU \cite{rexford}.

\textbf{Placement vs. routing:} Content placement is more powerful than routing because it can change the \emph{traffic matrix} for which the routing is to be computed. A traffic matrix is a 2-dimensional matrix representing the demand in the network. The $i,j$-th entry in this matrix is the traffic from node $i$ to node $j$ in the network topology \cite{fortz2000internet}.  Let us take an example traffic matrix for which routing is to be computed (Figure \ref{fig:placement-routing}). Content placement can turn any non-zero traffic matrix into a null matrix (one whose all entries are zero) provided all content that a node in a network needs is placed at the same node. Such a placement obviates the need to send traffic to any other node, and therefore makes routing a trivial problem. While this is an extreme example, and one may not have sufficient resources to place content at all locations in the network, this example demonstrates that the ability to change the traffic matrix makes content placement more powerful than routing.

@@
